\subsubsection{Consumer expenditure on the internet}
This is one of the most important trends to be aware of and act upon, as the internet retailing continues to show record growth. The internet retailing has more than doubled in the years from 2009 - 2014\footnote{Euromonitor: Consumer lifestyles in Denmark}. This trend is expected to continue to increase and therefore it is very important for MUJI to prioritise their presence online, the webshop and the visual identity of the company.  

\subsubsection{Tea is the future}
According to Euromonitor, tea, and especially japanese and chinese green tea, is the new coffee for danes \cite[29]{ConsumerLifestyles}. MUJI tea is apparently not available in EU or US according to the associated webshops, but the webshop for MUJI in Hong Kong\footnote{https://www.muji.com.hk/en/sub-category.php?dept=123&id=113&c=005} sell it. I think this trend is an obvious opportunity for MUJI to attract more consumers. My recommendation in order to take advantage of this trend, is to open an in-store cafe offering a variety of tea when the shop in Copenhagen is launched.  

\subsubsection{Agnostic shoppers}
This trend is one of the reasons for my choice of positioning and pricing strategy. The agnostic shoppers are not only the young people, but I think, however, they make up for the majority. They are intrigued by innovation around value \cite[3]{Top10Trends}, which opens up another opportunity for MUJI. MUJI designers came up with a bath towel that has a next life, which can be used as a bath math, and finally, as a duster \cite{FutureGrowth}. This kind of innovative products is the essence of innovation around value, and MUJI should continue to play around with new use of traditional products.   

\subsubsection{Changemakers}
The last trend I recommend MUJI to be aware of, and to act upon, is the "Changemakers". Social causes and climate change gets more attention, and companies as well as individuals are more concerned about these problems \cite[14-17]{Top10Trends}. This trend can also be used to establish a competitive advantage. I do not have the impression that sustainability is an essential element for MUJI, but I recommend MUJI to spend more effort in this regard and focus on sustainability and CSR, in relation to the products as well as the advertising. According to the Executive, MUJI has a good relationship with the suppliers and they care about them\cite{FutureGrowth}, which I think should be a part of their identity.